% environment
\documentclass[11pt,a4paper]{moderncv}
\moderncvtheme[blue]{banking}
\nopagenumbers{}

\usepackage[T1]{fontenc}
\usepackage{inputenc}
\usepackage[scale=0.9]{geometry}
\usepackage{tabularx}
\usepackage{mathpazo}
\usepackage{graphicx}

% macro
\renewcommand*{\labelitemi}{-}

\newcolumntype{L}{>{\raggedright\arraybackslash}X}
\newcolumntype{C}{>{\centering\arraybackslash}X}
\newcolumntype{R}{>{\raggedleft\arraybackslash}X}

\newcommand*{\experienceentry}[5][1.5mm]{
    \subsection{#2} \vspace{-1.5mm}
    \begin{tabularx}{\textwidth}{LR}
        {\itshape #3} & {\itshape #4, #5}
    \end{tabularx}
    \par\addvspace{#1}
}

\newcommand*{\educationentry}[4][0.5mm]{
    \begin{tabularx}{\textwidth}{LR}
        {\bfseries #3} & {\bfseries #4} \\
    \end{tabularx}
    {\itshape #2}
    \par\addvspace{#1}
}

\newcommand*{\scoreentry}[3][2.5mm]{
    {\bfseries #2} \\
    {\itshape #3}
    \par\addvspace{#1}
}

% preamble
\firstname{Aleksa}
\familyname{Markovic}
\address{Kragujevac, Serbia}{}

% document
\begin{document}
\maketitle
\vspace{-9.0mm}
\begin{tabularx}{\textwidth}{C C C}
    \emailsymbol\enspace \emaillink{mar.aleksa98@gmail.com} & \githubsocialsymbol\enspace \href{https://github.com/Aleksa-Markovic}{Aleksa-Markovic} & \faLinkedin\enspace \href{https://www.linkedin.com/in/aleksa-markovic-a4397b133/}{Aleksa Markovic}
\end{tabularx}
\vspace{-2.0mm}

% left column
\begin{minipage}[t]{0.62\textwidth}
    \section{SUMMARY}
    As a dedicated developer with a bachelor degree in Software Engineering and more than 3 years of experience, I specialize in Python, focusing on data science and AI, with additional back-end development expertise. I am fluent in English and Serbian and have a passion for traveling, reading, learning, and technology. I am eager to advance my career in software engineering by joining a prominent company.

    \section{PERSONAL INFORMATION}
    \begin{itemize}
        \item Name: Aleksa
        \item Surname: Markovic
        \item Born: 19/09/1998
        \item Gender: Male (He/Him)
        \item Location: Kragujevac, Serbia
    \end{itemize}

    \section{EXPERIENCE}
    \experienceentry{Astora Serbia}{Python Developer}{September 2023 - October 2024}{Novi-Sad, Serbia/Remote}

    \textbf{Python development and Data Analysis}
    \begin{itemize}
        \item Developed various Python scripts for data analysis and gathering.
        \item Used multiple libraries for data processing and analysis.
        \item Worked on models to improve their stability and functionality
        \item Led several projects solo, achieving complete customer satisfaction.
        \item Fully focused on honing my Python skills and improving as a developer.
    \end{itemize}

    \vspace{1.0mm}
    
    \experienceentry{Power Lever}{Software Engineer}{August 2021 - September 2023}{Kragujevac, Serbia}

    \textbf{Software development and Automation}
    \begin{itemize}
        \item Worked on automating daily tasks of other team members.
        \item Developed back-end features for client websites to enhance customer experience.
        \item Wrote software for both in-house and external projects using Python, including implementing UI for some of them.
        \item Mainly focused on Python, utilizing libraries such as pandas, bs4, matplotlib, PyQt5, tkinter, requests, and threading.
        \item Used JavaScript for back-end development on Knack, where the website was hosted.
    \end{itemize}
    Reference contact: Andreja Janicijevic (Owner)

    \vspace{2.0mm}

\end{minipage}
\hfill
% right column
\begin{minipage}[t]{0.35\textwidth}
    \section{SKILLS}
    \begin{tabularx}{\textwidth}{>{\bfseries}l@{\hskip 3.5mm}L}
        Soft. Eng   & Python, Javascript, C\#, Bash           \\
        Back End    & Python, Javascript                      \\
        OS          & Windows, Linux (Arch, Ubuntu)           \\
        Misc.       & AWS, \LaTeX                             \\
        Soft Skills & Resilience, Attentiveness, Organization
    \end{tabularx}

    \section{EDUCATION}
    \educationentry{Bachelor in Software Engineering}{FIMEK University}{Novi Sad, Serbia}
    2020-2024\\ 
    Bachelor thesis: Creating AI models for use in Medical fields
    \par
    \vspace{3.0mm}
    \educationentry{High School - Mathematics Department}{Second Gymnasium}{Kragujevac, Serbia}

    \section{SCORES}
    \scoreentry{English Speaking Board: C1 English (ESB)}{27/06/2023}
    Pass with distinction


    \section{LANGUAGES}
    \begin{itemize}
        \item Serbian (Native)
        \item English (Fluent - C1)
    \end{itemize}

    \section{INTERESTS}
    \begin{itemize}
        \item Technology
        \item Learning Languages
        \item Astrophotography
        \item Travel
        \item Concerts
        \item Cooking
    \end{itemize}
\end{minipage}

\end{document}